Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-20 doc/JFLA2022/paper.tex
small corrections; add a README.md
Two typos and one addition.

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Hydras and Cie (Draft) \\
  Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq}

@@

The contrast between the simplicity of the statements above and the complexity of their proofs convinced us that it is a good thema for a commented library of formal proofs.

\begin{itemize}
\item We present complete proof scripts for the \textit{Coq} proof assistant~\cite{Coq}. These scripts may consulted and replayed by the reader.
\item Complex formalisations and proofs are explained in an
  electronic book~\cite{HydraBook}. Whenever various reasonable choices exist, we try to present and compare the alternatives.
  For instance, Figures~\vref{fig:Ex42E0} and \vref{fig:Ex42-schutte} show two radically different proofs of the equality
  $\omega+42+\omega^2=\omega^2$, the first one is a simple proof by computation, the second one shows how this equality
  is a consequence of the axioms of the set-theoretic model  by Kurt Schütte~\cite{schutte}. 
\item
  Reciprocally, we provide ``concrete'' examples of several formalisation and proof techniques: operational type classes, functions defined by  equations, dependently typed functions, etc.
\item It may be used as a library on ordinal numbers, for instance for proving termination properties.
  \end{itemize}

@@

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, weused the formalisation of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem \cite{OConnor05, Goedel}.
For this purpose, and above all by consideration of the scientific interest of this contribution, we chose to host and maintain this work within \textit{Coq-Community}.

>>>>

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Hydras and Cie  \\
  Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq}

@@

The contrast between the simplicity of the statements above and the complexity of their proofs convinced us that it is a good theme for a commented library of formal proofs.

\begin{itemize}
\item We present complete proof scripts for the \textit{Coq} proof assistant~\cite{Coq}. These scripts may consulted and replayed by the reader.
\item Complex formalisations and proofs are explained in an
  electronic book~\cite{HydraBook} (PDF document of over 280 pages). Whenever various reasonable choices exist, we try to present and compare the alternatives.
  For instance, Figures~\vref{fig:Ex42E0} and \vref{fig:Ex42-schutte} show two radically different proofs of the equality
  $\omega+42+\omega^2=\omega^2$, the first one is a simple proof by computation, the second one shows how this equality
  is a consequence of the axioms of the set-theoretic model  by Kurt Schütte~\cite{schutte}. 
\item
  Reciprocally, we provide ``concrete'' examples of several formalisation and proof techniques: operational type classes, functions defined by  equations, dependently typed functions, etc.
\item It may be used as a library on ordinal numbers, for instance for proving termination properties.
  \end{itemize}

@@

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, we used the formalisation of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem \cite{OConnor05, Goedel}.
For this purpose, and above all by consideration of the scientific interest of this contribution, we chose to host and maintain this work within \textit{Coq-Community}.
